Supplementary Materials And Methods

### 2021-02-19 Supplementary_mat_met.Rmd
final versions of supplementary files
updating supplementay_mat_met files

```{r, include=FALSE, message=FALSE, warning=FALSE}

@@

## 1.2 Sample+ Data set:

@@

# adding new location information:
clearclipfinal <- clearclipfinal %>% 
  bind_cols(hg38clearclip) %>% 
  rename(HG38build_loc = X1) %>% 
  mutate(Genom_build="hg18") %>%
  dplyr::select(cluster=cluster.ID, chromosome = chr, start_position, 
                end_position, strand = strand.y, hgnc_symbol, 
                Ensembl_Gene_Id =ensembl_gene_id, 
                Ensembl_Transcript_Id =ensembl_transcript_id, 
                target_seq = target.map, miRNA, 
                miR_seq = miR.map, 
                seed_type = 'seed match', Energy = MFE, 
                HG38build_loc, Genom_build, region)

@@

```{r eval=FALSE}
experimentalmirnagene <- experimentalmirnagene %>%
  dplyr::select(miRNA, Ensembl_Gene_Id, hgnc_symbol, Energy, seed_type_effect, region_effect) %>%
  distinct() %>%
  group_by(Ensembl_Gene_Id, miRNA) %>%
  mutate(
    seed_type_effect = ifelse(seed_type_effect == max(seed_type_effect),
                              seed_type_effect, 
                              max(seed_type_effect) ),
    Energy = ifelse(Energy == min(Energy), 
                    Energy, 
                    min(Energy)),
    region_effect = ifelse(region_effect == max(region_effect),
                           region_effect, 
                           max(region_effect) ) ) %>%
  distinct()
```

```{r, eval=FALSE}
# the data frame generated up to now should match the data frame used in manuscript so the output should be "zero" different rows.
setdiff(experimentalmirnagene,readRDS("data/experimentalmirnagene.RDS"))
```

>>>>

```{r message=FALSE, warning=FALSE, include=FALSE}

@@

```
## 1.2 Sample+ Data set:

@@

# adding new location information:
clearclipfinal <- clearclipfinal %>% 
  dplyr::bind_cols(hg38clearclip) %>% 
  rename(HG38build_loc = X1) %>% 
  dplyr::mutate(Genom_build="hg18") %>%
  dplyr::select(cluster=cluster.ID, chromosome = chr, start_position, 
                end_position, strand = strand.y, hgnc_symbol, 
                Ensembl_Gene_Id =ensembl_gene_id, 
                Ensembl_Transcript_Id =ensembl_transcript_id, 
                target_seq = target.map, miRNA, 
                miR_seq = miR.map, 
                seed_type = 'seed match', Energy = MFE, 
                HG38build_loc, Genom_build, region)

@@

```{r eval=FALSE}
experimentalmirnagene <- experimentalmirnagene %>%
  dplyr::select(miRNA, Ensembl_Gene_Id, hgnc_symbol, Energy, seed_type_effect, region_effect) %>%
  distinct() %>%
  group_by(Ensembl_Gene_Id, miRNA) %>%
  mutate(
    seed_type_effect = ifelse(seed_type_effect == max(seed_type_effect),
                              seed_type_effect, 
                              max(seed_type_effect) ),
    Energy = ifelse(Energy == min(Energy), 
                    Energy, 
                    min(Energy)),
    region_effect = ifelse(region_effect == max(region_effect),
                           region_effect, 
                           max(region_effect) ) ) %>%
  ungroup()%>%
  distinct()

saveRDS(experimentalmirnagene, file = "data/experimentalmirnagene.RDS")

```{r, eval=FALSE}
# the data frame generated up to now should match the data frame used in manuscript so the output should be "zero" different rows.
dplyr::setdiff(experimentalmirnagene,readRDS("data/experimentalmirnagene.RDS"))
```
